
\subsection{Introduction}

The goal of this module is to match (row,column) positions on the red strip
to the sky.  The output will be six linear transformation coefficients per
red frame.  The transformation is accomplished by matching stars found in
Make Star List to calibrated astrometric stars produced in the astrometric
pipeline and input to this one.

\subsection{Input}

\subsubsection{Astrometric standard stars}
Astrometric standards in great circle coordinates
\subsubsection{List of stars from the photometric postage stamps}
Stars from the photometric postage stamps in (row,col) coordinates.
\subsubsection{Frame Description}
We need the number of rows per frame (and maybe the starting row).
In addition, we need the approximate great circle coordinates of the
first and last frame.
\subsection{Output}
\subsubsection{Astrometric calibration}
Six linear coefficients per red frame that translate row,col in the run
to great circle coordinates.
\subsubsection{List of stars from the photometric postage stamps}
We will add great circle coordinate fields to this list.
\subsection{Modules}
The required modules are:
\begin{enumerate}
\item Find Approximate Transformation - take the great circle coordinates
of the first and last frames and a row number, and compute the
approximate great circle latitude.
\sitem Extract List - extract a list between two latitudes or between
two rows.
\sitem Find Transformation - takes two star lists and the approximate
translation and computes a set of linear transformation coefficients
\sitem Interpolate - takes a set of coefficients and their positions on
the scan line, and interpolates (extrapolates) to the coefficients for
each frame.  Experience will show us the most appropriate function to
fit, and whether we need to smooth the results in any way, or throw out
some of the data points.
\sitem Update Star List - uses interpolated transformation parameters
to add the great circle coordinates to the list of stars from the postage
stamps.
\end{enumerate}
\subsection{Algorithms}
The same algorithm will be used to match star list as are used in calc
offsets and the astrometric pipeline.
\subsection{Quality, Debugging, Resources}
