
\subsection{Introduction}

The postage stamps from a run need to be flatfielded and then have their
positions, brightnesses, and profiles measured (if they are of stars), or
they need to be discarded.  The flow in this module will be something like:
\begin{itemize}
\item {\it For each color}
\begin{itemize}
\item {\it For each postage stamp:}
\begin{itemize}
\item {\it Read in a postage stamp}
\item {\it Flatfield the postage stamp}
\item {\it Find position, add to list}
\item {\it Find parameters in PSF function, add to list}
\item {\it Calculate total integrated counts, add to list}
\end{itemize}
\item {\it End of stamp loop}
\end{itemize}
\item {\it End of color loop}
\end{itemize}

\subsection{Inputs}

\subsubsection{Postage Stamps}

We will need a complete set of postage stamps in all colors for the current
run.

\subsubsection{Flatfield Array}
\subsubsection{Parameters}

We will pass in parameters like how big the aperture should be for
photometry and at what radius the sky should be calculated.

\subsection{Outputs}

\subsubsection{Star Lists}

We will generate one star list for every color.
The star list will contain all of the parameters for every object in the
postage stamps, regardless of whether it is a star or not.  For each object,
we will know the row and column in the stripe, the parameters that give
us a best fit to our PSF functional form, and the integrated DN for the
object.  The great circle coordinates will be added to the list in the
Astrometric Parameters module.

\subsection{Algorithms}

The algorithms for this section are straighforward.  The only module
with decisions to be made is the point spread function functional form,
so that we can fit that function's parameters.  The way this pipeline
has been constructed, it will be difficult (but possible) to find residuals 
from a function, since that would mean we have to have the postage stamps
available during the Find PSF module, or we would have to know ahead
of time which "stars" to include in building up a residual map as we
go along.

\subsection{Quality, Debugging, Resources}
