\subsection{Introduction}

The objects are found separately in each color.  This module merges the
lists together into a single list of merged objects.  Using the transformations
calculated from the postage stamps, the objects' masks are compared.
Any masks that overlap in space are merged together into one object.  If
one object, for example, in r', overlaps with two objects in g', they will
all come out as part of one merged object.  The object masks are grown to
be the union of all of the pixels in which the object was detected in
object finding.  If, for example, the object was not detected in u', it
will still have an OBJECT1 created for it.  The atlas images in all colors
are grown to contain all of the pixels in the object mask (the atlas images
are rectangular).  All information about the original OBJECT1 structures
is lost.

\subsection{Input}

\subsubsection{Corrected frames}

Since the process will go back to the original region and grow the atlas
image, it needs the original regions.  The name of the tcl array containing
the regions and a tcl list of the indices are passed.

\subsubsection{Noise regions}

Since the process will go back to the original region and grow the atlas
image, it also needs to grow the noise regions.  The name of the tcl array 
containing the noise regions and a tcl list of the indices are passed.

\subsubsection{Star lists in each color}

This is the output of object finding, one list per color.  The list is
a CHAIN of type OBJECT1.  Again, it is
passed as the name of the tcl array containing the lists.

\subsubsection{Offsets}

This is the offsets calculated in Calculate Offsets

\subsection{Output}

\subsubsection{Merged object list}

The merged list (a CHAIN of type OBJC) is returned.  Every OBJC contains
an OBJECT1 in each color.
